Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2016-01-18 cordillera-cycle.tex
Typeset: rewrap figure and table captions.
Typeset: negative numbers and Ph.D. to PhD.

\begin{acknowledgements}
      Foremost, we would like to thank Shawn Marshall for providing
      a~detailed, constructive analysis of this study during J.~Seguinot's
      Ph.D. defence (September 2014). His comments were used to improve the
      model set-up. We are very thankful to Constantine Khroulev, Ed Bueler,
      and Andy Aschwanden for providing constant help and development with
      PISM. This work was supported by the Swedish Research Council~(VR)
      grant no.~2008-3449 to A.~P.~Stroeven and by the German Academic
      Exchange Service~(DAAD) grant no.~50015537 and a~Knut and Alice
      Wallenberg Foundation grant to J.~Seguinot. Computer resources were
      provided by the Swedish National Infrastructure for Computing (SNIC)
      allocation no.~2013/1-159 and~2014/1-159 to A.~P.~Stroeven at the
      National Supercomputing Center (NSC).
\end{acknowledgements}

@@

\begin{table*}
\caption{Parameter values used in the ice sheet model.}
\label{tab:params}
%\scalebox{.85}[.85]
{\begin{tabular}{llrl}
    \tophline
    Not.    & Name & Value & Unit \\
    \middlehline
    $\rho$  & Ice density
            & 910
            & \unit{kg\,m^{-3}} \\

@@

\begin{table*}
  \caption{%
Palaeo-temperature proxy records and scaling parameters yielding
           temperature offset time-series used to force the ice sheet model
           through the last glacial cycle (Fig.~\ref{fig:lr_ts}). $f$
           corresponds to the scaling factor adopted to yield last glacial
           maximum ice limits in the vicinity of mapped end moraines, and
           $T_{[32, 22]}$ refers to the resulting mean temperature anomaly
           during the period -32 to~-22\,\unit{ka} after scaling.}
\label{tab:records}
%\scalebox{.850}[.850]
{\begin{tabular}{l|ccc|ccc|l}
    \tophline
    Record & Latitude & Longitude & Elev. & Proxy & $f$ & $T_{[32, 22]}$
           & Reference\\
    & & & (\unit{m\,a.s.l.}) & & & (K) & \\
    \middlehline
    GRIP     &  72{\degree}35$^{\prime}$\,N   % 72.58 (decimal)
             &  37{\degree}38$^{\prime}$\,W   % 37.64 (decimal)
             & 3238
             & \chem{\delta^{18}O}
             & 0.37 & -5.8  % -16.4126 (before scaling)
             & \citet{Dansgaard.etal.1993} \\

    NGRIP    &  75{\degree}06$^{\prime}$\,N   % 75.10
             &  42{\degree}19$^{\prime}$\,W   % 42.32
             & 2917
             & \chem{\delta^{18}O}
             & 0.24 & -6.5  % -26.7098
             & \citet{Andersen.etal.2004} \\

    EPICA    &  75{\degree}06$^{\prime}$\,S   % 75.1
             & 123{\degree}21$^{\prime}$\,E   % 123.35
             & 3233
             & \chem{\delta^{18}O}
             & 0.64 & -5.9  % -9.2055
             & \citet{Jouzel.etal.2007} \\

    Vostok   &  78{\degree}28$^{\prime}$\,S   % 78.8
             & 106{\degree}50$^{\prime}$\,E   % 106.8
             & 3488
             & \chem{\delta^{18}O}
             & 0.74 & -5.9  % -7.9550
             & \citet{Petit.etal.1999} \\

    ODP~1012 &  32{\degree}17$^{\prime}$\,N
             & 118{\degree}23$^{\prime}$\,W
             & -1772
             & \chem{U^{K'}_{37}}
             & 1.61 & -6.1  % -3.7889
             & \citet{Herbert.etal.2001} \\

    ODP~1020 &  41{\degree}00$^{\prime}$\,N
             & 126{\degree}26$^{\prime}$\,W
             & -3038
             & \chem{U^{K'}_{37}}
             & 1.20 & -6.0 % -5.0000
             & \citet{Herbert.etal.2001} \\
    \bottomhline
\end{tabular}}
\end{table*}

>>>>

\begin{acknowledgements}
      Foremost, we would like to thank Shawn Marshall for providing
      a~detailed, constructive analysis of this study during J.~Seguinot's
      PhD defence (September 2014). His comments were used to improve the
      model set-up. We are very thankful to Constantine Khroulev, Ed Bueler,
      and Andy Aschwanden for providing constant help and development with
      PISM. This work was supported by the Swedish Research Council~(VR)
      grant no.~2008-3449 to A.~P.~Stroeven and by the German Academic
      Exchange Service~(DAAD) grant no.~50015537 and a~Knut and Alice
      Wallenberg Foundation grant to J.~Seguinot. Computer resources were
      provided by the Swedish National Infrastructure for Computing (SNIC)
      allocation no.~2013/1-159 and~2014/1-159 to A.~P.~Stroeven at the
      National Supercomputing Center (NSC).
\end{acknowledgements}

@@

\begin{table*}
\caption{%
      Parameter values used in the ice sheet model.}
\label{tab:params}
%\scalebox{.85}[.85]
{\begin{tabular}{llrl}
    \tophline
    Not.    & Name & Value & Unit \\
    \middlehline
    $\rho$  & Ice density
            & 910
            & \unit{kg\,m^{-3}} \\

@@

\begin{table*}
\caption{%
      Palaeo-temperature proxy records and scaling parameters yielding
      temperature offset time-series used to force the ice sheet model
      through the last glacial cycle (Fig.~\ref{fig:lr_ts}). $f$ corresponds
      to the scaling factor adopted to yield last glacial maximum ice limits
      in the vicinity of mapped end moraines, and $T_{[32, 22]}$ refers to
      the resulting mean temperature anomaly during the period $-$32
      to~$-$22\,\unit{ka} after scaling.}
\label{tab:records}
%\scalebox{.850}[.850]
{\begin{tabular}{l|ccc|ccc|l}
    \tophline
    Record & Latitude & Longitude & Elev. & Proxy & $f$ & $T_{[32, 22]}$
           & Reference\\
    & & & (\unit{m\,a.s.l.}) & & & (K) & \\
    \middlehline
    GRIP     &  72{\degree}35$^{\prime}$\,N   % 72.58 (decimal)
             &  37{\degree}38$^{\prime}$\,W   % 37.64 (decimal)
             & 3238
             & \chem{\delta^{18}O}
             & 0.37 & $-$5.8  % -16.4126 (before scaling)
             & \citet{Dansgaard.etal.1993} \\

    NGRIP    &  75{\degree}06$^{\prime}$\,N   % 75.10
             &  42{\degree}19$^{\prime}$\,W   % 42.32
             & 2917
             & \chem{\delta^{18}O}
             & 0.24 & $-$6.5  % -26.7098
             & \citet{Andersen.etal.2004} \\

    EPICA    &  75{\degree}06$^{\prime}$\,S   % 75.1
             & 123{\degree}21$^{\prime}$\,E   % 123.35
             & 3233
             & \chem{\delta^{18}O}
             & 0.64 & $-$5.9  % -9.2055
             & \citet{Jouzel.etal.2007} \\

    Vostok   &  78{\degree}28$^{\prime}$\,S   % 78.8
             & 106{\degree}50$^{\prime}$\,E   % 106.8
             & 3488
             & \chem{\delta^{18}O}
             & 0.74 & $-$5.9  % -7.9550
             & \citet{Petit.etal.1999} \\

    ODP~1012 &  32{\degree}17$^{\prime}$\,N
             & 118{\degree}23$^{\prime}$\,W
             & $-$1772
             & \chem{U^{K'}_{37}}
             & 1.61 & $-$6.1  % -3.7889
             & \citet{Herbert.etal.2001} \\

    ODP~1020 &  41{\degree}00$^{\prime}$\,N
             & 126{\degree}26$^{\prime}$\,W
             & $-$3038
             & \chem{U^{K'}_{37}}
             & 1.20 & $-$6.0 % -5.0000
             & \citet{Herbert.etal.2001} \\
    \bottomhline
\end{tabular}}
\end{table*}
